Synthetic Observations of Extremely High Velocity (EHV) SiO components in young molecular outflows

### 2014-02-07 PAPER/Paola_2/ms_ver3.tex
small text edit
tweak to rad trans section

\subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
The radiative transfer program used is LIME (LIne Modeling Engine;
\citealt{Brinch:2010p13078}), which  calculates line intensities based
on a weighted sample of randomly chosen points in a continuous 3D
model. The method of selecting these points is given in section
\ref{subsec:gridding}. At each of these points, the density of the
main collision partner (equivalent amount of H, given by n(H$_2$)+
n(HI), assuming that ionized Hydrogen does not collide with SiO), gas temperature, velocity, molecular abundances and turbulent velocity are specified. These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is between the points connected by this method that photon are allowed to propagate (fig.~\ref{grid}). The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch:2010p13078}) to exceed 1000 for 99\% of the points, ensuring that the simulation has converged on a stable level population. After 20 iterations the model is ray-traced in order to produce synthetic brightness maps. The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction.% (Fig.~\ref{points}).

@@

\subsection{Emission maps, spectra and PV diagrams}
\label{ssec:emspecpv}
The output obtained from the radiative transfer calculation is a data
cube with velocity being the third axis. This allows us to obtain
spectra and position velocity diagrams from these data cubes. 
Figure~\ref{empvspec90} shows outputs from the data
cube for SiO(2-1) in the reference run. 
The top left panel in the figure shows the emission map for the jet
directed downwards. The notable features are the knots close to the
base of the jet and the emission near the bow shock due to density
enhancement by cooling instability. The PV diagram shown in the top
right panel is obtained along the jet as indicated by the vertical magenta
line in the left panel. The velocities are shown in the X-axis. High velocity features
are clearly seen in regions corresponding to the knots in the emission
maps. These features fade along the jet as the knots also disappear in
the emission map. The region close to the bow shock also shows high
velocity features.
%

>>>>

\subsection{The radiative transfer code} \label{subsec:radiative_transfer_code}
The radiative transfer program used is LIME (LIne Modeling Engine;
\citealt{Brinch:2010p13078}), which  calculates line intensities based
on a weighted sample of randomly chosen points in a continuous 3D
model. The method of selecting these points is given in section
\ref{subsec:gridding}. At each of these points, the density of the
main collision partner (equivalent amount of H, given by n(H$_2$)+
n(HI), assuming that ionized Hydrogen does not collide with SiO and that atomic and molecular hydrogen have the same collisional cross secrions with SiO), gas temperature, velocity, molecular abundances and turbulent velocity are specified. These points are then smoothed by Lloyd's algorithm \citep{Lloyd1982} in order to minimise the variation in distance between points whilst keeping the same underlying distribution. These points are then connected by Delaunay triangulation and it is between the points connected by this method that photon are allowed to propagate (fig.~\ref{grid}). The level populations of the selected molecules are calculated at each of these points from collisional and radiative (de)excitation and the local radiation field is calculated. This is repeated 20 times with the populations of each level converging towards a single value. This number of iterations is sufficient for the signal to noise ratio of the level populations (as defined in \citealt{Brinch:2010p13078}) to exceed 1000 for 99\% of the points, ensuring that the simulation has converged on a stable level population. After 20 iterations the model is ray-traced in order to produce synthetic brightness maps. The average of ten separate runs was taken to minimise the artefacts in the output images, resulting from the grid construction.% (Fig.~\ref{points}).

@@

\subsection{Emission maps, spectra and PV diagrams}
\label{ssec:emspecpv}
The output obtained from the radiative transfer calculation is a data
cube with velocity being the third axis. This allows us to obtain
spectra and position velocity diagrams from these data cubes. 
Figure~\ref{empvspec90} shows outputs from the data
cube for SiO(2-1) in the reference run. 
The top left panel in the figure shows the emission map for the jet. The notable features are the knots close to the
base of the jet and the emission near the bow shock due to density
enhancement by cooling instability. The PV diagram shown in the top
right panel is obtained along the jet as indicated by the vertical magenta
line in the left panel. The velocities are shown in the X-axis. High velocity features
are clearly seen in regions corresponding to the knots in the emission
maps. These features fade along the jet as the knots also disappear in
the emission map. The region close to the bow shock also shows high
velocity features.
%
